Real Time Fluid Simulation \\ \smaller using Smoothed-Particle Hydrodynamics and OpenGL

### 2014-12-11 paper/paper.tex
Added intro paragraph and Astrophysics paper

\abstract{
	This paper talks about the implementation of a real time Fluid simulation displayed in OpenGL \dots blaaaaaaaaaaaaa
}

@@

\section{Introduction}
%
Hello World! This is how you can cite a paper \cite{realtimerendering} Let's go to a new line \\
Let's go to a new paragraph \par\medskip
Let's write a formula
\begin{align*}
	\sum_{i=0}^N \int_{-\infty}^\infty e^{-\frac{1}{2}x^2} \; dx
\end{align*}
%
It's not that hard ;)

>>>>

\abstract{
	This paper explores the field of Smooth Particle Hydrodynamics (SPH), starting at its 
beginnings as a tool to simulate astrophysical phenomena and following its evolution and 
implementation as a way to simulate fluids such as water. We will then give a brief 
mathematical background and ensuing algorithm of our SPH simulation followed by a detailed 
explanation of it.
}

@@

\section{Introduction}
%
\hspace{6 pt} Smoothed Particle Hydrodynamics (SPH) successfully simulates fluids by breaking up a 
fluid body into individual parts, or particles. These particles together form a particle 
system that simulates various gravitational forces. Fluid movement is simulated in the 
system by moving particles around any particle moved, simulating a rippling, wave effect.
\\
\hspace*{6 pt} The ripple effect is created by first calculating which particles are surrounding 
a particle moved, and these surrounding particles are moved according to the movement 
of the first particle moved. But SPH wasn't originally intended to simulate liquid 
substances, but astrophysical phenomena.
%

\section{History}
%
something
%
